Lexical Richness as a Lens: Exploring the Influence of Social Class on Authors' Writings

### 2024-03-16 paper/paper.qmd
Better visualization on posterior distribution

author_CTTR_rstanarm_multilevel |>
  spread_draws(`(Intercept)`, b[, group]) |>
  mutate(condition_mean = `(Intercept)` + b) |>
  ggplot(aes(y = group, x = condition_mean)) +
  stat_halfeye() +
  theme_minimal()
```

>>>>

author_CTTR_rstanarm_multilevel |>
  spread_draws(`(Intercept)`, b[, group]) |>
  mutate(condition_mean = `(Intercept)` + b) |>
  ggplot(aes(y = group, x = condition_mean, fill = group)) +
  stat_halfeye() +
  labs(x = "Conditional Mean", y = "Group") +
  theme(panel.background = element_rect(fill = "white"),
              panel.grid.major = element_line(colour = "grey"),
              plot.title = element_text(color = "black", size = 14, face = "bold"),
              axis.title = element_text(color = "black"))
```
